Ceph Parallel File System Evaluation Report

### 2013-08-22 ceph-initial.tex
add replication level test dataset and plots
add paper flow and organization into introduction

\section{Ceph RADOS Scaling: Initial Results}

@@

\subsection{Scaling on number of OSDs per server}

@@

\subsection{Scaling on number of OSD servers}

@@

\section{Ceph File System Performance: Initial Test}
\label{sec:ior-initial}
We used the synthetic IOR benchmark suite for file system level performance and
scalability test.
The particular parameter setup is show in Table \ref{tbl:ior}. Each client node
has 6 GB of physical memory, the block size is set so as to mitigate cache
effects. In addition, the test harness program issues the following commands
at the beginning of each test:

@@

\begin{Verbatim}
# sync
# echo 3 | tee /proc/sys/vm/drop_caches
\end{Verbatim}

>>>>

\section{Ceph Evaluation: Initial Results}
\label{sec:ceph-initial}

\subsection{Ceph RADOS Scaling}

@@

\subsubsection{Scaling on number of OSDs per server}

@@

\subsubsection{Scaling on number of OSD servers}

@@

\subsection{Ceph File System Performance}

We used the synthetic IOR benchmark suite for file system level performance
and scalability test.  The particular parameter setup is show in Table
\ref{tbl:ior}. Each client node has 6 GB of physical memory, the block size is
set so as to mitigate cache effects. In addition, the test harness program
issues the following commands at the beginning of each test:

@@

\begin{Verbatim}[fontsize=\small]
# sync
# echo 3 | tee /proc/sys/vm/drop_caches
\end{Verbatim}

### 2013-08-22 introduction.tex
add paper flow and organization into introduction

As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
file system evaluation. The goal of our study is to investigate the
feasibility of using the Ceph for our future HPC storage deployment.  This
report presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph is still a relatively
\textit{young} parallel file system and its code base is changing rapidly. In
between releases, we often experienced different stability and performance
outcomes.  We will try to make clear in the report when such changes occurred.

>>>>

As part of this effort, we set up a dedicated testbed within NCCS for the Ceph
file system evaluation. The goal of our study is to investigate the
feasibility of using the Ceph for our future HPC storage deployment.  This
paper presents our experience, results, and observations. While evaluating
our results, please keep in mind that Ceph is still a relatively
\textit{young} parallel file system and its code base is changing rapidly. In
between releases, we often experienced different stability and performance
outcomes.  We will try to make clear in the writing when such changes occurred.

This paper is organized as follows. Section~\ref{sec:testbed} gives an
overview on our general test and evaluation methodology as well as testbed
environment; Following it, Section~\ref{sec:baseline} establishes the baseline
performance and expectations for all critical components on the data path;
Section~\ref{sec:ceph-initial} discusses our early results bottom up: from
middle tier RADOS object layer to the file system-level. Then in
Section~\ref{sec:ceph-tuning} we highlight the investigative and tuning
effort, we compare results before and after, and how the process eventually
bring the system performance to a respectable state.
Section~\ref{sec:ceph-meta} present our preliminary findings on Ceph's
metadata performance. Finally, Section~\ref{sec:conclusion} summarizes our
findings, observations, and future works.
